Main Analysis

### 2025-02-11 Manuscript Analysis/main_analysis.Rmd

final_ple <- glmmTMB(effort_rating ~ trial_c + speaker + rep_acc + (trial_c|subject) + (trial_c|code), data = ple_data)
sjPlot::tab_model(final_ple,
                  pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]"),
                  dv.labels = "Perceived Listening Effort",
                  file = "Tables/ple_mod_unstd.html")

@@

```
```{r}

@@

>>>>

final_ple <- glmmTMB(effort_rating ~ trial_c + speaker + rep_acc + (trial_c|subject) + (trial_c|code), data = ple_data)
sjPlot::tab_model(final_ple,
                  pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]"),
                  dv.labels = "Perceived Listening Effort",
                  file = "Tables/ple_mod_unstd.html")
```

@@

##### Estimated Peak Differences

max_1 <- speaker_diff_df |>
  dplyr::filter(time_norm >= 950 & time_norm <=1200 ) |>
  dplyr::slice_max(est,n=1)

max_2 <- speaker_diff_df |>
  dplyr::filter(time_norm >= 2500 & time_norm <=3500 ) |>
  dplyr::slice_max(est,n=1)

max_values <- rbind(max_1, max_2) |>
  dplyr::select(time_norm, est, Type)

max_values |>
  dplyr::rename("Normed Time" = time_norm,
                "Estimated Difference" = est,
                "Contrast" = Type) |>
  gt::gt()

@@

##### Estimated Peak Differences

max_1 <- als_diff_df |>
  dplyr::filter(time_norm >= 1300 & time_norm <=1700 ) |>
  dplyr::slice_max(est,n=1)

max_2 <- als_diff_df |>
  dplyr::filter(time_norm >= 3500 & time_norm <=4000 ) |>
  dplyr::slice_max(est,n=1)

max_values <- rbind(max_1, max_2) |>
  dplyr::select(time_norm, est, Type)

max_values |>
  dplyr::rename("Normed Time" = time_norm,
                "Estimated Difference" = est,
                "Contrast" = Type) |>
  gt::gt()
